Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 5

    As for the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradient that reflects radial variation of 
    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
    information about the assembly history of stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
    As expected, all median color profiles show smooth and shallow negative 
    gradients, but we do not find evidence for mass-dependence here. 
    We also compare our results with the stacked color profiles from  
    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering the differences in response curves of HSC and SDSS filters, and 
    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
    consistent with those based on SDSS images. 
    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
    the low surface brightness outskirt of galaxy.
    \jenny{explain what the red-halo effect is}
    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
    therefore can help provide more accurate color estimates.
    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
    measurements could also ``smooth'' the color gradients.
    The relative steeper color profiles have been observed in very nearby massive 
    ETGs individually.  
    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
    (\citealt{Iodice2016}). 
    These individual profiles show similar color gradients with the HSC median ones.

>>>>

    As for the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradient that reflects radial variation of 
    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
    information about the assembly history of stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
    As expected, all median color profiles show smooth and shallow negative 
    gradients, but we do not find evidence for mass-dependence here. 
    We also compare our results with the stacked color profiles from  
    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering the differences in response curves of HSC and SDSS filters, and 
    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
    consistent with those based on SDSS images. 
    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
    The SDSS $i$-band suffers from the so-called ``red-halo'' effect
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}). 
    The $i$-band PSF has more prominent wing than the other bands that 
    artificially distributes more flux to the outskirt, and lead to redder color in 
    the low surface brightness outskirt of galaxy.
    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
    therefore can help provide more accurate color estimates.
    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
    measurements could also ``smooth'' the color gradients.
    The relative steeper color profiles have been observed in very nearby massive 
    ETGs individually.  
    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
    (\citealt{Iodice2016}). 
    These individual profiles show similar color gradients with the HSC median ones.
